Robotic Cart System

### 2021-05-10 parts/10-introduction.tex
Update 10-introduction.tex
Fixed figures in introduction

%======================================================================
\chapter{Introduction}
\label{ch: Chapter1}
%======================================================================

@@

\vspace*{12pt}
\noindent
One such method, shown in Fig. \ref{fig:CompaRob}, that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}. Another method, shown in Fig. \ref{fig:ShoppingSup}, that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}. Therein, in Fig. \ref{fig:SmartCart}, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.

\begin{figure}[b]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob Robot}
   \label{fig:CompaRob}
\end{figure}

\begin{figure}[b]
   \centering
   \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping Support Robot}
   \label{fig:ShoppingSup}
\end{figure}

\begin{figure}[b]
   \centering
   \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organized into six chapters:
\todo[inline]{This section should go at the end of the chapter.}

\begin{itemize}
    \item Chapter \ref{ch: Chapter1} discusses the background and goals of the project and what other similar projects have accomplished.
    \item Chapter \ref{ch: Chapter2} explains how the robotic cart system in this project is broken down fundamentally, and the components used to build the robot.
    \item Chapter \ref{ch: Chapter3} goes over the design of the parabolic reflector arrays and how they were set up on the robot.
    \item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms that were used to create the code to make the robot move.
    \item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
    \item Chapter \ref{ch: Chapter6} concludes the project work and discusses future endeavors on this project.
\end{itemize}

>>>>

%======================================================================
\chapter{Introduction}
\label{ch: intro}
%======================================================================

@@

\vspace*{12pt}
\noindent
One such method, shown in Fig. \ref{fig:CompaRob}, that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
\begin{figure}[H]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob Robot}
   \label{fig:CompaRob}
\end{figure}
Another method, shown in Fig. \ref{fig:ShoppingSup}, that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
\begin{figure}[H]
   \centering
   \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping Support Robot}
   \label{fig:ShoppingSup}
\end{figure}
Therein, in Fig. \ref{fig:SmartCart}, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
\begin{figure}[H]
   \centering
   \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
\begin{itemize}
    \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
    \item Chapter \ref{ch: sysArchitecture} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
    \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
    \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
    \item Appendix \ref{ch: coppSimModeling} goes through the steps to build and simulate the Budget Bot chassis in CoppeliaSim
\end{itemize}
